Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-06-30 manuscript/manuscript.tex
removed addressed comments

Continue with the case where $X_i$'s are independent but the parameters
are unspecified. Denote by
$F^{(b)}_n$ the empirical distribution of the $b$th bootstrap sample and let
$\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap 
sample. 
Using the bootstrap (asymptotic) theory, we can approximate the distribution of
$\sqrt{n}(F_n(x) - F(x; \theta_0))$ and
$\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$
by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$ and
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$, respectively.
Therefore, if we define
\begin{align*}
Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - F_n(x)) - 
               \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n)) \\
             &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
               \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
\end{align*}
then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
expected to approximate the distribution of $T_n$. 
%\eds{you have defined two $T_n$'s - perhaps different notation should be used
%to differentiate the $T_n$ in the Intro and the $T_n$ in Section 2.1?  At least
%clarify which $T_n$ you are referring to here.}\mc{addressed}
We note that the term
$\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
\citet{babu2004goodness}.

@@

\begin{proposition}\label{prop:Tnboot}
  As $1/l+l/n\rightarrow 0$,
  \[
    \big\vert \mathbb{P}(T_n^{(b)}\leq x \mid \{X_i: i = 1, \ldots, n\}) -
    \mathbb{P}(T_n\leq x) \big\vert
    \overset{a.s.}{\rightarrow} 0
  \]
  for any fixed $x$, where and $T_n^*$ is the the statistic computed 
  based on the bootstrap sample $\{X_i^{(b)}: i = 1, \ldots, n\}$.
\end{proposition}

\eds{Is $T_n^*$ the same as $T_n^{(b)}$?}  
\eds{Can we replace the $t$ index with $i$ 
to be consistent with earlier notation?  Or use $t$ earlier when introducing
time-series data? ($t$ is used in the Simulation section below.)}\mc{I replaced
everything with $i$, I wasn't sure when to use $X_i$ or $\{X_i\}$}
\eds{I think this is fine -- $t$ or $i$ would have worked, as long as it is 
consistently used within the time series sections.}

@@

%\eds{Replace $X_{1:n}$ with $\{X_i: i = 1, \ldots, n\}$ or $\{X_t: t = 1, \ldots, n\}$?}
%\mc{addressed}

>>>>

Continue with the case where $X_i$'s are independent but the parameters
are unspecified. Denote by
$F^{(b)}_n$ the empirical distribution of the $b$th bootstrap sample and let
$\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap 
sample. 
Using the bootstrap (asymptotic) theory, we can approximate the distribution of
$\sqrt{n}(F_n(x) - F(x; \theta_0))$ and
$\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$
by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$ and
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$, respectively.
Therefore, if we define
\begin{align*}
Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - F_n(x)) - 
               \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n)) \\
             &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
               \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
\end{align*}
then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
expected to approximate the distribution of $T_n$. 
We note that the term
$\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
\citet{babu2004goodness}.

@@

\begin{proposition}\label{prop:Tnboot}
  As $1/l+l/n\rightarrow 0$,
  \[
    \big\vert \mathbb{P}(T_n^{(b)}\leq x \mid \{X_i: i = 1, \ldots, n\}) -
    \mathbb{P}(T_n\leq x) \big\vert
    \overset{a.s.}{\rightarrow} 0
  \]
  for any fixed $x$, where and $T_n^b$ is the the statistic computed 
  based on the bootstrap sample $\{X_i^{(b)}: i = 1, \ldots, n\}$.
\end{proposition}

@@
